### 2025-06-16 thesis_julio/Chapter1/chapter1.tex
16jun

Elementary particle physics is the study of the particles at the most fundamental level, the constituents of the universe as well as the interactions between them which are called, electromagnetic force, nuclear weak force and nuclear strong force and there is also the gravity force but this one doesn't have a satisfactory quantum theory for it. Each of these forces are mediated by exchange particles, in the case of the electromagnetic force the mediator is the photon, for the strong force the gluons, for the weak force the bosons W and Z and for the gravity we have the hypothetical graviton.  \cite{Griff}

@@

Each of these forces have a mathematical description for the physical systems of these interactions using the Quantum Field Theory (QFT). The one that describes systems under the electromagnetic force is called Quantum Electrodynamics (QED) this force dictates the electronic structure of atoms being the low energy manifestation of the electromagnetic theory. For the strong force Quantum Chromodynamics (QCD) is the fundamental theory of strong interactions, this force is responsible of maintaining protons and neutrons together in the atomic nucleus. For the weak interactions there is no particular name in the same way as the previous two, this force is is carried by all quarks and leptons and is responsible for the $\beta$ Decay of some radioactive isotopes and nuclear processes of the sun. \cite{mppthomson}

Almost all the physical phenomena can be explained with only the electron, the electron neutrino, the proton and the neutron interacting with the electromagnetic force, the strong force and the weak one. When higher levels of energy are present new particles are observed, all of this is known as the elementary particles which are embodied in the standard model of particle physics that is by far the best theorical model that describes interaction of this elementary particles. Is divided into two categories the bosonic sector and the fermionic sector.  \cite{mppthomson}

@@

The fermionic sector contains particle the particles that make up all known matter in the universe and is divided into the leptons and the quarks, both of this particles are divided into three generations, each generation being heavier than the one before. For the leptons we have electron and Its neutrino for the first generation, the second generation is. the $\mu$ and Its neutrino and the third one is the $\tao$ with Its neutrino. In the case of quarks we have the quark up and the quark down for the first generation, the second generation que have the quark charmd and the quark strange and for the third generation que have the quark top and the quark bottom. The bosons are the mediator particles called the gauge bosons already mentions, the photon, the gluon, the bosons $W\pm$ and the boson Z. There is also de Higgs bosson, which is the last gauge bossons and It's the responsible to give mass to the other SM particles

@@

With N1 and N2 being the bunch intensity, f the revolution frecuency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions and assuming the densities are uncorrelated in all planes.  \cite{Lumvdm}

@@

it is related directly to the number of observed events $L_{int} \cdot \sigma_{p}$ number of events of interest.

@@

The PCC luminometer method consist in counting the average number of pixel clusters on the detector to measure luminosity. This occurs during a zero bias event, an event that is trigged by requiring only that two proton bunches cross at the CMS interaction point. Giving that the number of pixels in really big the probability that a pixel is being hit by two different tracks by the same bunch crossing is really small. The mean number of pixel clusters in a simulated zero bias event is in the order of 100 per pp collision. The number of pixel clusters per bunch crossing is linearly dependent on pileup and therefore an accurate measure of the instantaneous luminosity.\cite{PCC1} The mean number of pixel cluster per trigger is

>>>>

Elementary particle physics is the study of the particles at the most fundamental level, the constituents of the universe as well as the interactions between them which are called, electromagnetic force, nuclear weak force, nuclear strong force and there is also the gravity force but this one doesn't have a satisfactory quantum theory for it. Each of these forces are mediated by exchange particles, in the case of the electromagnetic force the mediator is the photon, for the strong force the gluons, for the weak force the bosons W and Z and for the gravity we have the hypothetical graviton.  \cite{Griff}

@@

Each of these forces has a mathematical description for the physical systems of these interactions using the Quantum Field Theory (QFT). The one that describes systems under the electromagnetic force is called Quantum Electrodynamics (QED) this force dictates the electronic structure of atoms being the low energy manifestation of the electromagnetic theory. For the strong force Quantum Chromodynamics (QCD) is the fundamental theory of strong interactions, this force is responsible for maintaining protons and neutrons together in the atomic nucleus. For the weak interactions there is no particular name in the same way as the previous two, this force is carried by all quarks and leptons and is responsible for the $\beta$ Decay of some radioactive isotopes and nuclear processes of the sun. \cite{mppthomson}

Almost all the physical phenomena can be explained with only the electron, the electron neutrino, the proton and the neutron interacting with the electromagnetic force, the strong force and the weak one. When higher levels of energy are present new particles are observed, all of this is known as the elementary particles which are embodied in the standard model of particle physics that is by far the best theoretical model that describes the interaction of these elementary particles. They are divided into two categories the bosonic sector and the fermionic sector.  \cite{mppthomson}

@@

The fermionic sector contains particle the particles that make up all known matter in the universe and is divided into the leptons and the quarks, both of these particles are divided into three generations, each generation being heavier than the one before. For the leptons we have the electron and Its neutrino for the first generation, the second generation is. the $\mu$ and Its neutrino and the third one is the $\tao$ with Its neutrino. In the case of quarks we have the quark up and the quark down for the first generation, the second generation que have the quark charmd and the quark strange and for the third generation que have the quark top and the quark bottom. The bosons are the mediator particles called the gauge bosons already mentions, the photon, the gluon, the bosons $W\pm$ and the boson Z. There is also de Higgs bosson, which is the last gauge bossons and It's the responsible to give mass to the other SM particles

@@

With N1 and N2 being the bunch intensity, f the revolution frequency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions and assuming the densities are uncorrelated in all planes.  \cite{Lumvdm}

@@

This is related directly to the number of observed events $L_{int} \cdot \sigma_{p}$ number of events of interest.

@@

The PCC luminometer method consist in counting the average number of pixel clusters on the detector to measure luminosity. This occurs during a zero bias event, an event that is triggered by requiring only that two proton bunches cross at the CMS interaction point. Giving that the number of pixels in really big the probability that a pixel is being hit by two different tracks by the same bunch crossing is really small. The mean number of pixel clusters in a simulated zero bias event is in the order of 100 per pp collision. The number of pixel clusters per bunch crossing is linearly dependent on pileup and therefore an accurate measure of the instantaneous luminosity.\cite{PCC1} The mean number of pixel cluster per trigger is

### 2025-06-16 thesis_julio/Chapter3/chapter3.tex
16jun

For obtaining the importnat parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 kHz but the proton densities $\rho_{1}$ and $\rho{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities. The luminosity integral evaluated with the beams separated by a distance $\Delta_{x}$ and $\Delta_{y}$ can take the form of:

@@

Similarly to the previous step we can obtain the value of the other factor of (3.2) with an analogous process. The integrals resulting on the right side can be evaluated by evaluated by obtaining the rate in function of the beam-beam separation which are $\Delta x$ and $\Delta y$  this because the luminosity has a linear relationship with the rate. The Luminosity can be expresed on terms of the rate during the head on points using the following:

\begin{equation}
L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}}){\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
\end{equation}

@@

\begin{equation}
\Sigma_{x} = \frac{1}{2 \pi} \frac{\int R(\Delta x, \Delta y_{0} d(\Delta x) )}{R(\Delta x_{0}, \Delta y_{0})}
\end{equation}

@@

\begin{equation}
\sigma_{vis} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(\Delta x_{0} \Delta y_{0})}{N_{1} N_{2}f}
\end{equation}

@@

@@

For the calibration of 2024 in the LHC fill 9639 during may 15 to may 16 at collision proton proton with a energy of 13.6 TeV, the vdm scans were made there were a total of 5 vdm X and vdm Y scans and 2 beam img X and beam img Y and the Super Separation period which is a scan used to obtain a background estimation, this were the scans used on this analysis to compute the value of $\singa_{visible}$. The figure (3.x) shows a DOROS image of the fill and all the scans that were made during that period of time.

\begin{figure}[h]
    \centering
    \includegraphics[width=1\textwidth, height=0.4\textheight]{scans.png}
    \caption{Fill 9639 scans}
    \label{fig:scans}
\end{figure}

The 5 vdm scans vdM1, vdM2..., vdM5 are the scans usually used in the calibration to compute $\simga_{visible}$ two beams are separated the transverse bunch size and then scanned across one another in sequence of 25 steps with 30 seconds per step. The beam imaging scan is kept on a nominal position while the other is separated and scanned in 19 steps, the scan is performed first in the X direction and then in the Y direction. The Super Separation scans separates the beams a distance were the overlap of the beams is negligible, the minimum possible.

@@

The background estimation were obtained using the 5 Super Separation scans, the time on which this super separations were used was on UNIX time each of these super separations lasted a total of 5 minutes in the following table we got more information about the start and ending of the scans.

@@

\begin{figure}[H]
    \centering
    \includegraphics[height=0.4\textheight, width=0.8\textwidth]{sshist.png}
    \caption{SS periods histograms showing entries for bcid 345}
    \label{fig:SShist}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[height=0.30\textheight,width=1\textwidth]{SSmean.png}
    \caption{Mean per bcid}
    \label{fig:SSmean}
\end{figure}

In principle this value is a single value so we obtain a histogram obtaining a mean for all the mean values for all the 60 values this is shown in the following image:

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{ssthist.png}
    \caption{Histogram of all means}
    \label{fig:Histogram}
\end{figure}

With this que obtained that the value for super separation is $ss_{background}$ = 0.0251 +-0.0018 this value would be extracted from the PCC rates during the fit for the vdm scans.

@@

A few corrections were taken into consideration to eliminate noise data from another sources during this vdm calibration, this corrections are applied by the vdm framework.

@@

There are different fit models at the time to do the vdm calibration, the most common one is Single Gaussian but also other models like the Double Gaussian, QG, Poly2g or Poly 4G. Each of these models have different parameters and restrictions making some of them better than other on the fit quality.

For the main calibration we used the QG fit this fit uses the parameter $\sigma$, the peak and a q values as the parameters. This fit is given by the following equation:

\begin{equation}
f_{qg}(x,y) = peak e_{q}(-\beta(x - mean)^{2},q)
\end{equation}

@@

\begin{equation}
e_{q}(x) = (1+(1-q)x)^{\frac{1}{1-q}}
\end{equation}

q being a parameter and peak the maximum rate.

This fit model were applied to the data using vdmfamework software for all bcids, the following image shows this fit on the x plane and on the y plane on one bcid other bcids showed a similar result.

@@

To see if the fit converged we check the covariance matrix with the covalue, if this value is 3 the fit converge as we can see in the following image all of the bcids converged in all of the scans for the vdm and BI. 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{QG_covStatus.png}
    \caption{Covariance value showing that all bcids converged with the fit}
    \label{fig:QGfit}
\end{figure}

Also to see the fit quality we obtain the value of $\chi^{2}$ divided by the numbers of degree freedom the following image shows this:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{QG_chi2.png}
    \caption{Fit quality values}
    \label{fig:QGchi2}
\end{figure}

@@

The beam parameters of the vdm scan were obtained after the vdm framework run on the fit, one of the parameters obtained is the peak:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{QG_peak.png}
    \caption{QG peak values important on the computing of $\sigma_{visible}$}
    \label{fig:QGpeak}
\end{figure}

Here we can see that the peak values are increasing with the time which doesn't have sense since the number of particles through time should be lower, this behavior is then explained if we observe the results for the $\Sigma_{x, y}$ in the following image:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{QG_CapSigma.png}
    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
    \label{fig:QGcapsigma}
\end{figure}

Here we see that the $\Sigma_{x, y}$ values are decreasing for each scan reducing the thickness of the beams and thus observing a higher peak value even if the number of particles is decreasing through time.

Now with all the values obtained we can compute the value of $sigma_{visible}$, the values for each bcid is shown on the following image:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{sigbcid.png}
    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
    \label{fig:sigbcid}
\end{figure}

We are expecting a constant value of $\sigma_v{visible}$ here it appears to be changing each scan this could be to other uncertainties. Then in the following image we show the result for the weighted mean of the $\sigma_{visible}$ for each scan:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{sigscan.png}
    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
    \label{fig:sigscan}
\end{figure}

@@

\newpage

\section{Systematics}

We obtained a systematic uncertainties comparing the fit made but with different corrections, in the following table we check this uncertanties with citing a relative change per correction:

\begin{table}[H]
\begin{center}
\small
\begin{tabular}{|c c c|} 
 \hline
 Correction & $\sigma_{visible}$ & Relative Change(\%) \\ [0.5ex] 
 \hline\hline
 No correction & $1452589 \pm 2041$ & - \\ 
 \hline
 Background & $1448801 \pm 676$ & \\
 \hline
 Background + Ghost Satellite & $1450154 \pm 560$ & \\
 \hline
 Background + Ghost Satellite + Beam Beam + Dynamic Beta & $1460890 \pm 546$ & \\ [1.0ex]
 \hline
\end{tabular}
\caption{Comparison of $\sigma_{visible}$ values with different corrections}
\end{center}
\end{table}

>>>>

For obtaining the important parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 kHz but the proton densities $\rho_{1}$ and $\rho{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities. The luminosity integral evaluated with the beams separated by a distance $\Delta_{x}$ and $\Delta_{y}$ can take the form of:

@@

Similarly to the previous step we can obtain the value of the other factor of (3.2) with an analogous process. The integrals resulting on the right side can be evaluated by evaluated by obtaining the rate in function of the beam-beam separation which are $\Delta x$ and $\Delta y$  this because the luminosity has a linear relationship with the rate. The Luminosity can be expresed on terms of the rate during the head on positions, R(\Delta_{x0}, \Delta_{y0}) like in the equation (3.5)

\begin{equation}
L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}){\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}}
\end{equation}

@@

\begin{equation}
\Sigma_{x} = \frac{1}{2 \pi} \frac{\int R(\Delta x, \Delta y_{0}) d(\Delta x) )}{R(\Delta x_{0}, \Delta y_{0})}
\end{equation}

@@

\begin{equation}
\sigma_{vis} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(\Delta x_{0}, \Delta y_{0})}{N_{1} N_{2}f}
\end{equation}

@@

This scans were analyzed using the vdM framework, a CMS tool to obtain different parameters using a fit model on the vdM scans, this framework read hd5 files and with a set of instructions the value of $\sigma_{visible}$ can be obtained.

@@

For the calibration of 2024 in the LHC fill 9639 during may 15 to may 16 at collision proton proton with a energy of 13.6 TeV, the vdm scans were made there were a total of 5 vdm X and vdm Y scans and 2 beam img X and beam img Y and the Super Separation period which is a scan used to obtain a background estimation, this were the scans used on this analysis to compute the value of $\sigma_{visible}$. The figure (3.x) shows a DOROS image of the fill and all the scans that were made during that period of time.

\begin{figure}[h]
    \centering
    \includegraphics[width=1\textwidth]{scans.png}
    \caption[Doros for fill 9639]{DOROS beam position during LHC Fill 9639 for the vdM scans. Horizontal and vertical beams are shown over time}
    \label{fig:scans}
\end{figure}

The 5 vdm scans vdM1, vdM2..., vdM5 are the scans usually used in the calibration to compute $\sigma_{visible}$ two beams are separated the transverse bunch size and then scanned across one another in sequence of 25 steps with 30 seconds per step. The beam imaging scan is kept on a nominal position while the other is separated and scanned in 19 steps, the scan is performed first in the X direction and then in the Y direction. The Super Separation scans separates the beams a distance were the overlap of the beams is negligible, the minimum possible.

@@

The background estimation were obtained using the 5 Super Separation scans, the time on which this super separations were used was on UNIX time, this time can be defined as a system for tracking a point in time as the number of seconds that have happened since January 1 at 00:00 in universal time (UTC). Each of these super separations lasted a total of 5 minutes in the following table we got more information about the start and ending of the scans.

@@

\begin{figure}[H]
    \centering
    \includegraphics[height=0.4\textheight, width=0.8\textwidth]{sshist.png}
    \caption{Distribution of average PCC for bcid 345 during SS number 2. The PCC values are computed in NB4 time intervals.}
    \label{fig:SShist}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{SSmean.png}
    \caption{This plot shows the evolution of the PCC value for the twelve differents bcids during the SS periods, it also shows the mean of each bcid.}
    \label{fig:SSmean}
\end{figure}

In principle this value is a single value so we obtain a histogram obtaining a mean for all the mean values for all the 60 values as It's shown on figure (3.6)

\begin{figure}[H]
    \centering
    \includegraphics[height = 0.45 \textwidth ,width=1\textwidth]{ssthist.png}
    \caption{This plots shows an histogram with all SS values for all bcids, the mean of all this values is used as the final result.}
    \label{fig:Histogram}
\end{figure}

With this it was obtained that the value for super separation is $ss_{background}$ = 0.0251 +-0.0018 this value will be removed from the PCC rates during the fit for the vdm scans.

@@

A few corrections were taken into consideration to eliminate noise data from another sources during this vdm calibration, this corrections are applied by the vdM framework.

@@

There are different fit models at the time to do the vdm calibration, the most common one is Single Gaussian but also other models like the Double Gaussian, QG, Poly2G or Poly4G. Each of these models have different parameters and restrictions making some of them better than other on the fit quality.

For the nominal calibration we used the QG fit model this fit model uses the parameter $\beta$, the peak value which is the maximum rate obtained during the head on period, the mean and a q values which is also a parameter. This fit model is given by the following equation:

\begin{equation}
f_{qg}(\Delta x) = peak * e_{q}(-\beta(\Delta x - mean)^{2},q)
\end{equation}

@@

\begin{equation}
e_{q}(x, q) = (1+(1-q)x)^{\frac{1}{1-q}}
\end{equation}

This fit model were applied to the data using vdM famework software for all bcids, the figure (3.7) shows this fit on the x plane and on the y plane for one bcid. Other bcids showed a similar result.

@@

To see if the fit converged we check the status of the covariance matrix if this value is 3 the fit is converged as we can see in the figure (3.8) shows all of the bcids converged in all of the scans for the vdm and BI. 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{QG_covStatus.png}
    \caption{Status of the covariance matrix gives 3 for all values showing that all bcids converged with the fit}
    \label{fig:QGfit}
\end{figure}

Also to see the fit quality we obtain the value of $\chi^{2}$ divided by the numbers of degree freedom this graphic is shown on the figure (3.9).

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{QG_chi2.png}
    \caption{Chi2 values to see the fit quality, the green line represent the mean}
    \label{fig:QGchi2}
\end{figure}

\section{Fit model optimization}

Two fit models were used for this, the first one described above and the second Poly2G. The poly2G model consist on a value r2 which is a parameter, the value $\Sigma$ related to the beam width, the peak which is the maximum rate during the head on period and the mean. Its defined as:

\begin{equation}
f_{Poly2G}(\Delta x) = peak * ( 1 + r_2 \left( \frac{x - mean}{\sigma / (1 + r_2)} \right)^2 \right) \exp\left( -\frac{1}{2} \left( \frac{x - mean}{\sigma / (1 + r_2)} \right)^2 \right)
\end{equation}

Once the Poly2G fit model was used the chi2 value was compared with the nominal fit model, in the figure (3.9) we can see the chi2 values for each scan. The mean value of the chi2 is lower than the QG that's the reason we used it as the nominal fit model.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{poly2g.jpeg}
    \caption{Chi2 values to see the fit quality of the poly2g fit model the green line represent the mean, notice that the mean is lower than with the nominal fit model.}
    \label{fig:QGchi2}
\end{figure}

@@

The beam parameters of the vdm scan were obtained after the vdM framework run whit the QG fit model one of the parameters obtained is the peak value, figure 3.12 shows the peak values obtained with the fits to the different vdM scans.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{QG_peak.png}
    \caption{QG model fit peak values obtained for the different scans in X and Y.}
    \label{fig:QGpeak}
\end{figure}

Here we can see that the peak values are increasing with the time in the fill, this behavior is then explained if we observe the results for the $\Sigma_{x, y}$ shown in the figure (3.13). Here we see that the $\Sigma_{x, y}$ values are decreasing for each scan reducing the thickness of the beams and thus observing a higher peak value even if the number of particles is decreasing through time.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{QG_CapSigma.png}
    \caption{QG model fit $\Sigma$ values obtained for the different scans in X and Y in the vdM fill.}
    \label{fig:QGcapsigma}
\end{figure}

\section{Results}

After the obtention of the beam parameters  the value of $\sigma_{visible}$ can be obtained, the values for each bcid is shown are shown on the image (3.13).

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{sigbcid.png}
    \caption{The value of $\sigma_{visible}$ of all twelve bcids and the seven used scans}
    \label{fig:sigbcid}
\end{figure}

We are expecting a constant value of $\sigma_{visible}$ here it appears to be changing each scan this could be to other uncertainties. Then in the image (3.14) Its shown the result on each scan for the weighted mean which is a mean taken into consideration a value mean that is defined as:

\begin{equation}
w_{i}=\frac{1}{\sigma^{2}}
\end{equation}

So then the weighted mean value of $\sigma_{visible}$ would be:

\begin{equation}
\sigma_{vis} = \frac {\Sigma_{i} w_{i} \sigma^{i}_{vis}}{\Sigma_{i} w_{i}} 
\end{equation}

With the error defined as:

\begin{equation}
\sigma_{visErr} = \frac{1}{\sqrt{\Sigma_{i} w_{i}}}
\end{equation}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{sigscan.png}
    \caption{$\sigma_{visible}$ weighted mean per each scan}
    \label{fig:sigscan}
\end{figure}

@@

The uncertainties from systematics are also taken into consideration, the uncertainties taken in consideration are the one from Background noise, the one from Scan to scan variation and the bunch to bunch variation.

Starting for the Background there were analysis made with the QG model fit which doesn't extract the background PCC, the sigma visible obtained in this case was of $\sigma_{visnobg}$ = 1452589 compared to the value that we obtained $\sigma_{vis}$ = 1450890 can be concluded that the uncertainty is 0.11\%.

In the case of scan to scan variation the standard deviation of the seven scans is taken as uncertainty with a value of 0.30\%.

For the bunch to bunch uncertainty the value of $\sigma_{vis}$ was obtained on each scan to each value there is a standard deviation assigned which is divided by the mean of the twelve BCIDS. This value is then divided by the square root of the number of bunches, all of this results are show in in the table (3.2). The uncertainty value was 0.02\%.

\begin{table} [H]
\begin{center}
\caption{Bunch to bunch uncertainty table.}
\begin{tabular}{|c c c c|} 
 \hline
 Scan & \sigma_{vis} & STD & Syst. Error  \\ [0.5ex] 
 \hline\hline
 vdM1 & 1463330 & 1220 & 0.02  \\ 
 \hline
 vdM2 & 1453795 & 1212 & 0.02 \\
 \hline
 vdM3 & 1464237 & 953 & 0.01 \\
 \hline
 vdM4 & 1454363 & 1170 & 0.02 \\
 \hline
 vdM5 & 1465271 & 1200 & 0.02  \\ 
 \hline
 BI1 & 1457208 & 1169 & 0.02 \\ 
 \hline
 BI2 & 1464367 & 1233 & 0.02\\
 \hline
 vdM6 &1462515  & 1155 & 0.02 \\ 
 \hline
    \textbf{mean}        &             &            & 0.2 \\ [1.0ex]
 \hline
\end{tabular}
\end{center}
\end{table}

The sum between all the uncertainties can be see in detail in the table (3.3), the total systematic uncertainty is 0.43\% (6281) taking into consideration only those systematic uncertainties.

\begin{table} [H]
\begin{center}
\caption{Systematic uncertainties total.}
\begin{tabular}{|c c|} 
 \hline
 Systematic  & Systematic uncertainty \\ [0.5ex] 
 \hline\hline
 Background & 0.11\%   \\ 
 \hline
 Bunch to Bunch & 0.02\%  \\
 \hline
 Scan to scan & 0.30\% \\
 \hline
  Total          &     0.43\%  \\ [1.0ex]
 \hline
\end{tabular}
\end{center}
\end{table}

%\begin{table}[H]
%\begin{center}
%\small
%\caption{Comparison of $\sigma_{visible}$ values with different corrections}
%\begin{tabular}{| c| c| c|} 
 %\hline
 %Correction & $\sigma_{visible}$ & Relative Change(\%) \\ [0.5ex] 
 %\hline\hline
% No correction & $1452589 \pm 2041$ & - \\ 
 %\hline
% Background & $1448801 \pm 676$ & +0.26 \\
 %\hline
 %Background + Ghost Satellite & $1450154 \pm 560$ & -0.09 \\
 %\hline
% Background + Ghost Satellite + Beam Beam + Dynamic Beta & $1460890 \pm 546$ & -0.74 \\ [1.0ex]
 %\hline
%\end{tabular}
%\end{center}
%\end{table}

### 2025-06-16 thesis_julio/Chapter4/chapter4.tex
16jun

The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 \pm 546$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.

>>>>

The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 \pm 546 \pm 6281(systematics)$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.
